Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-16 GWLDCII.tex
final changes from on the phone

Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
\begin{dfn} \label{proporderingdfn}
  The ordering of the propagators on $W = (\cP, [n])$ defined by $I_i^W$ is the ordering in which they contribute to the algorithm as it constructs $I_i^W$.
%  $\cP = \{p_1, \ldots p_k\}$, where 
% \[I_i = \{I_i(p_1) <_i I_i(p_2) <_i \ldots <_i I_i(p_k)\}.\]
% (The superscript $W$ is omitted here to simplify the notation.)\note{Sian tweaked this slightly to emphasise the $<_i$ order, because standard convention in most papers is to write all GN terms in the 1-order.}
\end{dfn}

Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I^W_i$, making the above ordering well defined.

Note that different $I^W_*$ impose different orderings on the propagators. Furthermore, Lemma \ref{no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$. That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.

@@

\begin{rmk} \label{clockwise ordering rem}
When $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e. any other propagator in $\cP \setminus \cP_{m-1}$ that is supported on $a_m$ must be inside $p_m$ in the $a_m-1$ ordering.
\end{rmk} \sanote{We use this fact at least twice below}

>>>>

%Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
\begin{dfn} \label{proporderingdfn}
  There is an ordering on the propagators on $W = (\cP, [n])$ defined by $I_i$. This is the ordering in which they contribute to the algorithm as it constructs $I_i$.
%  $\cP = \{p_1, \ldots p_k\}$, where 
% \[I_i = \{I_i(p_1) <_i I_i(p_2) <_i \ldots <_i I_i(p_k)\}.\]
% (The superscript $W$ is omitted here to simplify the notation.)\note{Sian tweaked this slightly to emphasise the $<_i$ order, because standard convention in most papers is to write all GN terms in the 1-order.}
\end{dfn}

Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I_i$, making the above ordering well defined.
Note that different $I_*$ impose different orderings on the propagators. Furthermore, Lemma \ref{lem no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$. That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.

@@

\begin{rmk} \label{clockwise ordering rem}
When $p$ contributes $I_i(p) = a$, it must be the clockwise-most propagator amongst those not yet assigned that is supported on $a$ i.e. any propagator assigned later that is supported on $a$ must be inside $(p, <_{a-1})$.
\end{rmk} \sanote{We use this fact at least twice below}
